Privacy-Preserving Localization Using Private Linear-Combination Aggregation

### 2021-05-21 main.tex
Removed the proof summary image as it is not so important in the appendix

\section{LCAO Scheme Proof} \label{app:proof}
The scheme in section \ref{sec:lcao_scheme} will be shown to meet LCAO by contrapositive. We show that for an adversary $\mathcal{A}$ playing against a challenger using the scheme, we can always create an adversary $\mathcal{A}'$ playing against a challenger $\mathcal{C}$ using the Joye-Libert scheme, such that
\begin{equation*}
    \mathsf{Adv}^{LCAO}(\mathcal{A}) > \eta_1(\kappa) \implies \mathsf{Adv}^{AO}(\mathcal{A}') > \eta_2(\kappa)\,,
\end{equation*}
for some negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$. That is, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure (which is not the case \cite{joyeScalableSchemePrivacyPreserving2013}). The reduction has been summarised visually in figure \ref{fig:proof_summary}.
\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize,scale=0.95]
    % Bounding box
    \draw [gray] (0,0) rectangle (6.5,6.5);

    % Outer adversary rectangle
    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.5);
    % Inner adversary rectangle
    \draw[rounded corners=15pt, fill=gray!60] (0.5,6) rectangle (6,5);

    % Adversaries and challenger
    \node at (3.25,3) {\Large$\mathcal{A}'$};
    \node at (3.25,5.5) {\Large$\mathcal{A}$};
    \node at (3.25,0.5) {\Large$\mathcal{C}$};

    % Arrows
    \node[text width=3cm, align=center] at (2,1) {Joye-Libert\\AO secure\\scheme};
    \draw [-latex] (2,1.75) -- (2,2.5);

    \node[text width=3cm, align=center] at (2,3.75) {Our\\LCAO secure\\scheme};
    \draw [-latex] (2,4.5) --(2,5);

    \node[text width=3cm, align=center] at (4.5,3.75) {``Break''\\Our scheme};
    \draw [-latex] (4.5,5) -- (4.5,4.5);

    \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
    \draw [-latex] (4.5,2.5) -- (4.5,1.75);
\end{tikzpicture}
\caption{Summary of our LCAO security proof.}
\vspace{-\baselineskip}
\label{fig:proof_summary}
\end{figure}
\begin{proof}
    Consider adversary $\mathcal{A}$ playing the LCAO game. The following is a construction of an adversary $\mathcal{A}'$ playing the AO game \cite{shiPrivacyPreservingAggregationTimeSeries2011} against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme.
    \begin{LaTeXdescription}
        \item[Setup] When receiving $N$ and $H$ as public parameters from $\mathcal{C}$, choose an $m>1$ and give public parameter $H$, number of weights $m$, and $pk_0=N$ to $\mathcal{A}$.
        \item[Queries] Handle queries from $\mathcal{A}$:
        \begin{LaTeXdescription}
            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $\rho_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions 
            \begin{equation*}
                (N+1)^{\omega^{(t)}_{j}}\rho_j^N\pmod{N^2},\,1\leq j\leq m
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for the instance $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$. The received response will be of the form $(N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $\rho^N$ for a random $\rho \in \mathbb{Z}_N$ and return 
            \begin{equation*}
                (N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho^N H(t)^{sk_i} \pmod{N^2}
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Compromise Query}] When $\mathcal{A}$ submits compromise query $i$, make the same compromise query $i$ to $\mathcal{C}$, and return the recieved secret key $sk_i$ to $\mathcal{A}$.
        \end{LaTeXdescription}
        \item[Challenge] When $\mathcal{A}$ submits challenge series
        \begin{equation*}
            \left\langle\left(i,t^*,a^{(t^*)(0)}_{i,1},\dots,a^{(t^*)(0)}_{i,m}\right)\,\middle|\,i \in S\right\rangle
        \end{equation*}
        and
        \begin{equation*}
            \left\langle\left(i,t^*,a^{(t^*)(1)}_{i,1},\dots,a^{(t^*)(1)}_{i,m}\right)\,\middle|\, i \in S\right\rangle\,,
        \end{equation*}
        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for instance $t^*$ and submit AO challenge series
        \begin{equation*}
            \left\langle\left(i,t^*,\sum^m_{j=1}a^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i \in S\right\rangle
        \end{equation*}
        and
        \begin{equation*}
            \left\langle\left(i,t^*,\sum^m_{j=1}a^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i \in S\right\rangle\,,
        \end{equation*}
        to $\mathcal{C}$. The received response will be of the form 
        \begin{equation*}
            \left\langle(N+1)^{\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}H(t^*)^{sk_i}\,\middle|\,i\in U\right\rangle\,,
        \end{equation*}
        for an unknown $b \in \{0,1\}$. Multiply series elements by $\rho_i^N,\,1 \leq i \leq n$ for randomly chosen $\rho_i \in \mathbb{Z}_N$ and return
        \begin{equation*}
            \left\langle(N+1)^{\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}\rho_i^N H(t^*)^{sk_i}\,\middle|\,i\in U\right\rangle
        \end{equation*}
        to $\mathcal{A}$.
        \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to~$\mathcal{C}$.
    \end{LaTeXdescription}

>>>>

\section{LCAO Scheme Proof} \label{app:proof}
The scheme in section \ref{sec:lcao_scheme} will be shown to meet LCAO by contrapositive. We show that for an adversary $\mathcal{A}$ playing against a challenger using the scheme, we can always create an adversary $\mathcal{A}'$ playing against a challenger $\mathcal{C}$ using the Joye-Libert scheme, such that
\begin{equation*}
    \mathsf{Adv}^{LCAO}(\mathcal{A}) > \eta_1(\kappa) \implies \mathsf{Adv}^{AO}(\mathcal{A}') > \eta_2(\kappa)\,,
\end{equation*}
for some negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$. That is, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure (which is not the case \cite{joyeScalableSchemePrivacyPreserving2013}).
\begin{proof}
    Consider adversary $\mathcal{A}$ playing the LCAO game. The following is a construction of an adversary $\mathcal{A}'$ playing the AO game \cite{shiPrivacyPreservingAggregationTimeSeries2011} against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme.
        \item[Setup] When receiving $N$ and $H$ as public parameters from $\mathcal{C}$, choose an $m>1$ and give public parameter $H$, number of weights $m$, and $pk_0=N$ to $\mathcal{A}$.
        \item[Queries] Handle queries from $\mathcal{A}$:
            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $\rho_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions 
            \begin{equation*}
                (N+1)^{\omega^{(t)}_{j}}\rho_j^N\pmod{N^2},\,1\leq j\leq m
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for the instance $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$. The received response will be of the form $(N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $\rho^N$ for a random $\rho \in \mathbb{Z}_N$ and return 
            \begin{equation*}
                (N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho^N H(t)^{sk_i} \pmod{N^2}
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Compromise Query}] When $\mathcal{A}$ submits compromise query $i$, make the same compromise query $i$ to $\mathcal{C}$, and return the recieved secret key $sk_i$ to $\mathcal{A}$.
        \item[Challenge] When $\mathcal{A}$ submits challenge series
        \begin{equation*}
            \left\langle\left(i,t^*,a^{(t^*)(0)}_{i,1},\dots,a^{(t^*)(0)}_{i,m}\right)\,\middle|\,i \in S\right\rangle
        \end{equation*}
        and
        \begin{equation*}
            \left\langle\left(i,t^*,a^{(t^*)(1)}_{i,1},\dots,a^{(t^*)(1)}_{i,m}\right)\,\middle|\, i \in S\right\rangle\,,
        \end{equation*}
        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for instance $t^*$ and submit AO challenge series
        \begin{equation*}
            \left\langle\left(i,t^*,\sum^m_{j=1}a^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i \in S\right\rangle
        \end{equation*}
        and
        \begin{equation*}
            \left\langle\left(i,t^*,\sum^m_{j=1}a^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i \in S\right\rangle\,,
        \end{equation*}
        to $\mathcal{C}$. The received response will be of the form 
        \begin{equation*}
            \left\langle(N+1)^{\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}H(t^*)^{sk_i}\,\middle|\,i\in U\right\rangle\,,
        \end{equation*}
        for an unknown $b \in \{0,1\}$. Multiply series elements by $\rho_i^N,\,1 \leq i \leq n$ for randomly chosen $\rho_i \in \mathbb{Z}_N$ and return
        \begin{equation*}
            \left\langle(N+1)^{\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}\rho_i^N H(t^*)^{sk_i}\,\middle|\,i\in U\right\rangle
        \end{equation*}
        to $\mathcal{A}$.
        \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to~$\mathcal{C}$.
